---
name: Brian
surname: Muchmore
profilepic: avatar.jpg
position: "Resident Physician"
aboutme: "Resident in the combined Pediatrics-Medical Genetics program at the University of Michigan, Ann Arbor."
address: "University of Michigan, Ann Arbor"
phone: 240-408-6061
www: brianmuchmore.com
email: "bmuchmore@gmail.com"
github: bmuchmore
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 3873B3
docname: CV/Resume
output: vitae::moderncv
---

```{r, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
library(dplyr)
library(RefManageR)
library(readr)
library(stringr)
```

```{r, include = FALSE}
# muchmore_b_pubmed <- ReadPubMed("Muchmore B", database = "PubMed")
# other_pubmed <- ReadPubMed("A cytokine network profile delineates a common", database = "PubMed")
# bm_pubmed <- append(muchmore_b_pubmed, other_pubmed)
# bm_pubmed_latex <- toBibtex(bm_pubmed)
# write_lines(bm_pubmed_latex, "C:/Users/MediaPC/Desktop/cv_vitae/raw.bib")
# bib_entry <- ReadBib("C:/Users/MediaPC/Desktop/cv_vitae/raw.bib", check = FALSE)
# bib_df <- as.data.frame(bib_entry)
# corrected_bib_df <- bib_df %>%
#   mutate(author = str_replace_all(.[["author"]], "c\\(", "")) %>%
#   mutate(author = str_replace_all(.[["author"]], "\\)", "")) %>%
#   mutate(author = str_replace_all(.[["author"]], '\\"', "")) %>%
#   mutate(author = str_replace_all(.[["author"]], "\\{", "")) %>%
#   mutate(author = str_replace_all(.[["author"]], "\\}", "")) %>%
#   mutate(author = str_replace_all(.[["author"]], "\\\\", "")) %>%
#   mutate(author = str_replace_all(.[["author"]], "\\Ã\\³", "o")) %>%
#   mutate(author = str_replace_all(.[["author"]], "\\Ã\\¡", "a")) %>%
#   mutate(author = str_replace_all(.[["author"]], "\\Ã\\º", "u")) %>%
#   mutate(author = str_replace_all(.[["author"]], "\\Ã", "i")) %>%
#   mutate(author = str_replace_all(.[["author"]], "\\i\\±", "n")) %>%
#   mutate(author = str_replace_all(.[["author"]], "\\i\\¶", "o")) %>%
#   mutate(author = str_replace_all(.[["author"]], "\\i\\«", "e")) %>%
#   mutate(author = str_replace_all(.[["author"]], "i\\©", "e")) %>%
#   mutate(author = str_replace_all(.[["author"]], "i\\¨", "e")) %>%
#   mutate(author = str_replace_all(.[["author"]], "'", "-")) %>%
#   mutate(journal = str_replace_all(.[["journal"]], "\\s*\\([^\\)]+\\)", "")) %>%
#   mutate(journal = str_replace_all(.[["journal"]], ":.*", "")) %>%
#   mutate(title = str_replace_all(.[["title"]], "\\Ã\\Ž\\Â\\»", "L")) %>%
#   arrange(desc(year))
# bib_df_authorships <- corrected_bib_df %>%
#   slice(-1, -2, -4, -5, -7) %>%
#   as.BibEntry()
# bib_df_collaborations <- corrected_bib_df %>%
#   slice(1, 2, 4, 5, 7) %>%
#   as.BibEntry()
# WriteBib(bib_df_authorships, file = "C:/Users/MediaPC/Desktop/cv_vitae/brian_authorships.bib")
# WriteBib(bib_df_collaborations, file = "C:/Users/MediaPC/Desktop/cv_vitae/brian_collaborations.bib")
```

# Skills

 * 10,000+ hours of laboratory bench work experience.
 * 10,000+ hours of data science experience with working proficiency in R, Bash, and Python.
 * Professional proficiency using Docker, Traefik and Guacamole.

# Education

```{r}
tribble(
  ~Degree, ~Year, ~Institution, ~Where,
  "Resident", "06/2021-present", "University of Michigan Combined Pediatrics-Medical Genetics Program", "Ann Arbor, Michigan",
  "M.D.", "08/2017-05/2021", "Robert Larner, M.D., College of Medicine at the University of Vermont", "Burlington, Vermont",
  "B.S. in Pre-medicine", "09/2009-09/2012", "University of Maryland", "College Park, Maryland",
  "B.A. in Russian Studies", "08/2002-06/2006", "Bates College", "Lewiston, Maine"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Lapses in Training

```{r}
tribble(
  ~Institution, ~Where,
  "Period between medical school graduation and the beginning of residency", "05/24/2021-06/20/2021"
) %>% 
  detailed_entries(Institution, Where)
```

# Awards

```{r}
tribble(
  ~Year, ~Desc,
  "05/2020", "Jerold and Ingela Lucey Early Career Investigator Prize for Innovations in Infant or Child Health"
) %>% 
  detailed_entries(Desc, Year)
```

# Certification/Licensure

```{r}
tribble(
  ~Year, ~Type,
  "Basic Life Support", "10/2018",
  "Advanced Cardiovascular Life Support", "11/2021"
) %>% 
  detailed_entries(Year, Type)
```

# Volunteer Experience

```{r}
tribble(
  ~Degree, ~Year, ~Institution, ~Where,
  "Camp Fantastic", "08/2012-08/2016", "Volunteer at a sleep-away camp for children with cancer, which is sponsored by the NIH and run by the organization Special Love", "Front Royal, Virginia"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Work Experience

```{r}
tribble(
  ~Degree, ~Year, ~Institution, ~Where,
  "CodoniX", "01/2016-01/2021", "Real-time reporting and data mining of Codonix’s terabyte-plus of patient data", "Potomac, Maryland"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Research Experience

```{r}
tribble(
  ~Degree, ~Year, ~Institution, ~Where,
    "Research Fellow at GENyO in the laboratory of Dr. Marta Alarcón-Riquelme", "01/2015-01/2019", "Lead bioinformatician for the PRECISESADS Flow Cytometry Study Group, which was a subgroup of a multi-national and multi-institutional project to find clinically useful biomarkers for systemic autoimmune diseases. Also, lead bioinformatician and co-laboratory leader of Spain’s first CyTOF/Helios core facility", "Granada, Spain",
  "CyTOF/CODEX Course Attendee", "05/2018-05/2018", "Was a participant in the 2018 CyTOF/CODEX mini-course held by the Nolan laboratory at Stanford University in order to help set-up Spain's first CyTOF/Helios core facility. Airfare, accommodation and training fees were provided by the PRECISESADS project", "Palo Alto, California",
  "Research Fellow at Chulalongkorn University in the laboratory of Dr. Yong Poovorawan", "01/2013-01/2014", "Evolutionary analysis of SNPs and INDELs using ancient genomes and 1000 genomes data", "Bangkok, Thailand",
  "Cancer Research Training Award Fellow at the National Institutes of Health in the laboratory of Dr. Ludmila Prokunina-Olsson", "09/2009-09/2012", "Functional investigation of GWAS cancer signals associated with HCV-related traits and bladder cancer", "Bethesda, Maryland",
  "Research Internship at the National Institutes of Health in the laboratory of Dr. Alasdair Steven", "05/2009-09/2009", "Cloned mutants of the fungal prion protein Het-s for analysis of structural motifs with electron microscopy", "Bethesda, Maryland",
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Publications

```{r}
bibliography_entries("brian_authorships.bib") %>%
  arrange(desc(issued))
```

# PRECISESADS Flow Cytometry Study Group Collaborations

```{r}
bibliography_entries("brian_collaborations.bib") %>%
  arrange(desc(issued))
```

# Poster Presentations

```{r}
tribble(
  ~Degree, ~Year, ~Institution, ~Where,
  "Muchmore, B., Le Lann, L., Jamin, C., consortium PRECISESADS, Marañon, C., Pers, J.O., & Alarcon-Riquelme, M.E.", "03/2017 Annals of the Rheumatic Diseases", "02.16 Machine learning of flow cytometry data encompassing seven systemic autoimmune diseases and controls.", "Athens, Greece",
    "Muchmore, B., Tang, W., Porter-Gill, P., Kohaar, I., Liu, L., Brand, N., Park, H., Dickensheets, H., Sheikh, F., Rehermann, B.,Donnelly, RP., O'Brien, T.R., & Prokunina-Olsson L.", "09/2013 International Cytokine and Interferon Society", "182 : Identification and characterization of interferon-lambda-4 (IFN-lambda-4), a novel class-2 cytokine which impairs clearance of hepatitis C virus", "San Francisco, California",
  "Muchmore, B., Park, H., Dickensheets, H., O'Brien, T. R., Rehermann, B., Donnelly, R., & Prokunina-Olsson L.", "04/2011 AACR 102nd Annual Meeting", "Abstract 3751: Expression analysis of the IL28A, IL28B, IL29 and IL28L genes in primary human peripheral blood mononuclear cells and hepatocytes: Effects of activation mode, time-course and genotypes", "Orlando, Florida"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Oral Presentations

```{r}
tribble(
  ~Degree, ~Year, ~Institution, ~Where,
    "University of Vermont Pediatric Grand Rounds", "05/2020", "Real-time monitoring of influenza and COVID-19 in urgent cares across the United States", "Burlington, Vermont",
  "PRECISESADS General Assembly", "03/2017", "Real-time machine learning of OMICS data", "Suresnes, Spain",
  "Conference of Complex Diseases", "03/2016", "CymeR: Cytometry analysis using KNIME, Docker and R.", "Granada, Spain",
  "KNIME Spring Summit", "02/2016", "Dockerizing KNIME - Recipes for a KNIME cocktail", "Berlin, Germany"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Hobbies & Interests

```{r}
tribble(
  ~Hobby,
  "Woodworking, aquaponics, soccer and the R programming language."
) %>% 
  brief_entries(
    Hobby
  )
```

# Language Fluency

```{r}
tribble(
  ~Language, ~Language_Proficiency, ~Proficiency_Description,
  "English", "Native", "I converse easily and accurately in all types of situations.",
  "Russian", "Basic", "I speak the language imperfectly and only to a limited degree and in limited situations.",
  "Spanish", "Basic", "I speak the language imperfectly and only to a limited degree and in limited situations.",
  "Thai", "Basic", "I speak the language imperfectly and only to a limited degree and in limited situations."
) %>% 
  brief_entries(
    Language,
    Language_Proficiency,
    Proficiency_Description
  )
```

# Other Awards/Accomplishments

```{r}
tribble(
  ~Degree, ~Year, ~Institution, ~Where,
  "Patent", "01/2020", "NOVEL INTERFERON-(lambda)-4 (IFNL-4) PROTEIN, RELATED NUCLEIC ACID MOLECULES, AND USESTHEREOF.", "Ref: E-217-2011-1. U.S. Pat: 10,545,147"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

